Optimal updating factor in adaptive flat-distribution simulations

### 2016-04-26 doc/invt.tex
k-limited optimal schedule
fix key legend

\subsection{\label{sec:results_invt}
Inverse-time schedule}

We tested the theory of computing errors
on the simple inverse-time schedule,
%
\begin{equation}
\alpha(t) = \frac{1}{\lambda \, (t + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
where $\lambda$ is a free parameter,
and $t_0$ is given by Eq. \eqref{eq:t0_sinc}.
%and $t_0 = 2/\alpha_0$.
%
The error of this schedule
can be computed analytically
(cf. Appendix \ref{sec:invt_schedule}),
and tested against simulation.

@@

>>>>

\subsection{\label{sec:results_invt}
Modified inverse-time schedule}

We tested the theory of computing errors
on the modified inverse-time schedule,
%
\begin{equation}
\alpha(t) = \frac{1}{\lambda \, (t + t_0) },
\label{eq:alpha_invtlambda}
\end{equation}
%
where $\lambda$ is a free parameter,
and $t_0$ is given by Eq. \eqref{eq:t0_sinc}.
%and $t_0 = 2/\alpha_0$.
%
The error of this schedule
can be computed analytically
(cf. Appendix \ref{sec:invt_schedule}),
and tested against simulation.

@@

For the Gaussian updating scheme,
we listed the errors from different schedules,
in Table \ref{tab:error_Gaussian}.
%
Clearly,
the optimal schedules yielded the smallest errors.

\begin{table}[h]
  \caption{\label{tab:error_Gaussian}
    Error of the Gaussian updating scheme of $\sigma = 10$.
    $t_0$ is given by Eq. \eqref{eq:t0_sinc}.
    \note{ Use the simulation data.  }%
  }
  \setlength{\tabcolsep}{5pt}
  \begin{tabular} { l | p{2cm} p{2.5cm} p{1.8cm} }
    \hline
      Schedule
    &
      Inverse-time, Eq. \eqref{eq:alpha_invt1}
    &
      Modified inverse-time,
      Eq.~\eqref{eq:alpha_invtlambda} 
      with optimized $\lambda$
    &
      Optimal,
      Eq. \eqref{eq:q_opt}
    \\
    \hline
    Global
    &
    $4.2 \times 10^{-6}$
    &
    $7.1 \times 10^{-7}$
    &
    $2.7 \times 10^{-7}$
    \\
    \hline
    Local
    &
    $3.7 \times 10^{-4}$
    &
    $1.7 \times 10^{-4}$
    &
    $9.1 \times 10^{-5}$
    \\
    \hline
  \end{tabular}
\end{table}

To verify Eq. \eqref{eq:half_alpha0},
we computed the optimal schedules
for different values of $q(T)$,
and plotted the final error
against the initial updating magnitude, $\alpha(0)$.
%
As shown in Fig. \ref{fig:erriascan},
The minimal error is reached at
$\alpha(0) = \alpha/2 = 5 \times 10^{-5}$.

\begin{figure}[h]
\begin{center}
  \makebox[\linewidth][c]{
    \includegraphics[angle=0, width=1.0\linewidth]{fig/erriascan.pdf}
  }
  \caption{
    \label{fig:erriascan}
    Relative error
    versus the initial updating magnitude, $\alpha(0)$,
    for optimal schedules with different $q(T)$.
    Assuming the Gaussian updating scheme
    with $\sigma = 10$,
    and $\alpha_0 = 10^{-4}$.
    %
    The points were obtained from averaging results
    from 1000 independent simulations;
    the curves are theoretical predictions.
    %
    \note{This figure was produced by
      \texttt{doc/fig/erriascan.gp}.
      The data were saved under
      \texttt{data/iascan}.
    }%
  }
\end{center}
\end{figure}
